RadLib: a radiative property model library for CFD

### 2021-09-08 manuscript/manuscript.tex
revision 1 submitted
Second round of revisions in response to reviewer comments.

%% This list environment is used for the references in the
%% Program Summary
%%
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{float}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{bm}
\usepackage{seqsplit}
\usepackage{enumitem}

@@

\newcommand{\BS}{\boldsymbol}
\setlist[itemize]{noitemsep}%, topsep=0pt}

@@

For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
% 
\begin{linenomath}
\begin{equation} \label{e:RTE_general}
    \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
\end{equation}
\end{linenomath}
%
where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$. Solving the RTE requires information about the radiative properties of the materials and media in the system. Radiative property data typically takes the form of radiation absorption coefficients $\kappa$, which are provided by a radiation property model. Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, and depends on the local thermochemical state of the system (e.g., temperature, pressure, and composition). Radiation property models, including those implemented in RadLib, are typically developed using high-resolution spectral databases like HITRAN and HITEMP \cite{Rothman_2010} in order to calculate spectral absorption coefficients, thus reducing or simplifying the huge amount of spectral data by using correlations and modeling assumptions \citep{Zhang_2002b}.

The direct solution of the spectral RTE using so-called line-by-line calculations in which the RTE is solved for each individual spectral line is computationally prohibitive for most practical configurations and is used primarily for model validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly incorporated into the RTE.
%VBS: citation here?
Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential absorption bands, but these cant lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.

@@

At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients using the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model. These models were chosen for their relevance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

@@

@@

The Planck Mean (PM) model is the simplest of the three models implemented. This model assumes a single gray gas and computes the absorption coefficient as a function of temperature, pressure, and gas composition.

@@

For each species, the PM model provides the absorption coefficient as fourth or fifth order polynomial fits in one or two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}. See \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}. The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)

@@

The gray gas weight $a_j$ is the fraction of blackbody emission from the set of wavenumbers $\Delta_j$ that correspond to a given cross-section band $j$. Weights are computed using the absorption line blackbody distribution function (ALBDF) \cite{Pearson_2014}, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorption cross sections smaller than an arbitrary absorption cross-section $C$: 
%
\begin{linenomath}
    \begin{equation} \label{e:albdf}
        F(C,\BS{\phi},T) = \frac{1}{\sigma T^4}\int_{\{\eta:\,C_\eta(\eta,\BS{\phi})<C\}}E_b(\eta,T)d\eta,
\end{equation}
\end{linenomath}
%
where $\phi$ represents the thermodynamic state, $\sigma$ is the Stefan-Boltzmann constant, $T$ is temperature, and $E_b(\eta,T)$ is the blackbody emission at a given wavenumber $\eta$ and temperature $T$.
As a result, a specific gray gas weight $a_j$ can be calculated as the difference between the ALBDF values at its cross-section boundaries:
%
\begin{linenomath}
    \begin{equation}\label{e:aj}
    a_j = F(\tilde{C}_j,\BS{\phi}, T) - F(\tilde{C}_{j-1}, \BS{\phi},T).
\end{equation}
\end{linenomath}
%
%todo: deal with T versus Tb in e:albdf and previous eqn.
Note that $F$ varies between zero and one and is monotonic in $C$, which permits calculation of an inverse ALBDF $C(F,\BS{\phi},T)$.

@@

The RCSLW model uses rank correlation as follows.
Consider Eq.~\ref{e:albdf} evaluated at an arbitrary reference temperature $T_r$ for thermodynamic states $\phi_1$ and $\phi_2$ as detailed above:
% $C=\hat{C}_1$, $\BS{\phi}=\BS{\phi}_1$, $T=T_r$, and again at$C=\hat{C}_2$, $\BS{\phi}=\BS{\phi}_2$, $T=T_r$, where $T_r$ is some reference temperature:
%
\begin{linenomath}
    \begin{align} \label{e:albdf2}
        F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
        F(\hat{C}_2,\BS{\phi}_2,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_2}E_b(\eta,T_r)d\eta.
    \end{align}
\end{linenomath}
%
Since $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$ are rank correlated (by definition), $H_1=H_2$ and we have 
%
\begin{linenomath}
    \begin{equation}\label{e:FeqF}
    F(\hat{C}_1,\BS{\phi}_1,T_r)=F(\hat{C}_2,\BS{\phi}_2,T_r).
\end{equation}
\end{linenomath}
%
Recall that the ALBDF can be inverted, so if $\hat{C}_1$ and $\BS{\phi}_1$ are known, we can compute $F=F(\hat{C}_1,\BS{\phi_1},T_r)$ and then invert $F$ to obtain $\hat{C}_2$ at $\BS{\phi}_2$. Note that Eq.~\ref{e:FeqF} holds for arbitrary states $\BS{\phi}_1$ and $\BS{\phi}_2$, so any known $F=F(C,\BS{\phi},T)$ can be inverted to get $C$ at the corresponding state $\BS{\phi}$.

@@

The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, \texttt{lib} containing library files for each interface, \texttt{cmake} with relocatable CMake files for downstream usage, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
\begin{itemize}
    \item \texttt{rad\textunderscore planck\textunderscore mean.h},
    \item \texttt{rad\textunderscore wsgg.h},
    \item \texttt{rad\textunderscore rcslw.h},
    \item \texttt{rad\textunderscore module.mod}.
\end{itemize}
%
The C++ and Fortran libraries in the \texttt{lib} folder are
\begin{itemize}
    \item \texttt{libradlib.a},
    \item \texttt{libradlib\textunderscore fortran.a}.
\end{itemize}
%
This folder also contains the Python module. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation, for example, \texttt{\seqsplit{export\ PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.

@@

Table~\ref{t:examples} summarizes the example cases. Each case is labeled according to its source---Solvojov et al. \cite{Solovjov_2017} (S), Bordbar et al. \cite{Bordbar_2020} (B), or Solovjov et~al. \cite{Solovjov_2001} (Sb)---and the number of each example corresponds to the example number in its respective reference. Each example case consists of one or more gas layers (``slabs'') bounded by black walls. 
Example S1 consists of two adjacent gas layers with identical species compositions: one hot layer of constant thickness and one cold layer of varying thickness. 
In Example S2, the two gas layers are isothermal but differ in the value of the \ce{CO2} mole fraction, where the layer thickness of the ``thin'' slab (with the smaller \ce{CO2} mole fraction) varies.
Example S3 applies parabolic temperature and \ce{H2O} mole fraction profiles across a single gas layer. 
Example S4 divides the gas into three equally-spaced layers and applies a triangular temperature profile to the middle layer and a constant temperature to the two outer layers.
Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K applied to a single gas layer of constant composition.
Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $x_{CO2}=1-x_{H2O}$). 
Example Sb1 consists of a single gas with a uniform temperature and composition profile and soot radiation. 
%
\begin{table}
    \caption{Summary of example cases. All cases use $P=1$ atm and black walls.}
    \label{t:examples}
    \centering
    \resizebox{\textwidth}{!}{
    \begin{tabular}{c l l c c c c}
        \hline
        Example & T(K)                          & $x_{H2O}$  $x_{CO2}$ (mole frac.)               & L (m)   & $T_{walls}$ (K) & Ref.\\
        \hline
        S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$    & $x_{CO2}=0.1$, $x_{H2O}=0.2$                    & 0.5-2.5 & cold, cold	& \cite{Solovjov_2017}     \\
        S2 & T=1000                             & $x_{CO2}(x<0.5)=0.4$, $x_{CO2}(x>0.5)=0.1$      & 0.5-2.5 & cold, cold & \cite{Solovjov_2017}    \\
           &                                    & $x_{H2O}=0.0$                                   &         &                \\
        S3 & $T(x) = 4000x(L-x)/L^2 + 800$      & $x_{H2O}(x) = 0.8x(L-x)/L^2 + 0.12$             & 1       & 800, 800 & \cite{Solovjov_2017}      \\
           &                                    & $x_{CO2}=0$                                     &         &                \\
        S4 & middle third triangular to 2500    & $x_{H2O}=0.1$, $x_{CO2}=0$                      & 0.3     & 500, 500 & \cite{Solovjov_2017}      \\
        S5 & $T(x) = 1000 + 500\cos(\pi x/L)$ 	 & $x_{H2O}=0.1$, $x_{CO2}=0$                      & 2       & 1500, 500 & \cite{Solovjov_2017}     \\
        B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$ & $x_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$	& 1       & 400, 400 & \cite{Bordbar_2020}      \\
           &                                    & $x_{CO2}=1-x_{H2O}$                             	&         &                \\
        Sb1& $T = 1000$                         & $x_{H2O} = 0.2$, $x_{CO2}=0.1$, $x_{CO}=0.03$   	& 1       & cold, cold & \cite{Solovjov_2001}    \\
        \hline
    \end{tabular}
    }
\end{table}
%

@@

Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}. These plots are included to demonstrate the examples that are provided with the code, and to compare the models to give an indication of their relative accuracy. In all examples, the RCSLW model data is computed using four gray gases ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Example S5, in which the number of gray gases in the RCSLW model is varied. The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature. 
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        Example S1 & Example S2 \\
        \includegraphics[width=2.75 in]{fig_ex_S1.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_S2b.pdf} \\
        Example S3 & Example S4 \\
        \includegraphics[width=2.75 in]{fig_ex_S3a.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_S4a.pdf} \\
        Example S5 & Example B3 \\
        \includegraphics[width=2.75 in]{fig_ex_S5c.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_B3.pdf}
    \end{tabular}
    \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}.}
    \label{f:examples}
    \end{center}
\end{figure}
%
\begin{figure}
    \begin{center}
        \includegraphics[width=5.5 in]{fig_ex_Sb1.pdf}
    \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
    \label{f:exSb1}
    \end{center}
\end{figure}
%

In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data. The results show that the PM model tends to exaggerate the trends displayed by the other models. The PM data mimics the shape of the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity. For the PM model in Example S5, $Q$ varies from around -80~kW/m$^3$ at $x=0$ to a peak of 200~kW/m$^3$ at x=$1.5$~m and drops to~100 kW/m$^3$ at $x=2$~m. 
In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36~m in the thick and thin layers, respectively. These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
Example S3 illustrates that the PM model tends to overpredict radiative heat loss at hight temperatures, which has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.

@@

The RadLib model was coupled to the Fire Dynamics Simulator (FDS) code developed at NIST \cite{FDS}. FDS is written in Fortran, and the Fortran interface of Radlib was used for simulations. FDS includes several radiative models, but the spectral WSGG model coupled to a finite volume discrete ordinates model is used here. This was done by editing the \texttt{radi.f90} file. A \texttt{use rad\textunderscore module} statement is included and the functions \texttt{A\textunderscore WSGG} and \texttt{KAPPA\textunderscore WSGG} were replaced with calls to RadLib's \texttt{get\textunderscore k\textunderscore a\textunderscore oneband}. The \texttt{oneband} version was used because FDS does an outer iteration over the bands/gases, computing properties at a given band for each grid point.

@@

RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property models in CFD simulations. At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients using the optically thin approximation, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. Each of the implemented models has been validated and the library's structure and functionality has been outlined. The library can be expanded to include additional property models.

>>>>

%% This list environment is used for the references in the
%% Program Summary
%%
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{float}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{bm}
%\usepackage{seqsplit}
%\usepackage{enumitem}

@@

\newcommand{\BS}{\boldsymbol}
%\setlist[itemize]{noitemsep}%, topsep=0pt}

@@

    For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
% 
    \begin{linenomath}
        \begin{equation}
            \label{e:RTE_general}
            \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
        \end{equation}
    \end{linenomath}
%
    where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity
    (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length
    along direction $\mathbf{s}$.
    Solving the RTE requires information about the radiative properties of the materials and media in the system.
    Radiative property data typically takes the form of radiation absorption
    coefficients $\kappa$, which are provided by a radiation property model.
    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, and depends
    on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
    Radiation property models typically consist of correlations between radiative properties and high-resolution
    spectral databases, reducing the huge amount of spectral data and
    simplifying evaluation of radiation absorption coefficients \cite{Zhang_2002b}.

    The direct solution of the spectral RTE using so-called line-by-line calculations in which the RTE is solved for each
    individual spectral line is computationally prohibitive for most practical configurations and is used primarily for model
    validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly
    incorporated into the RTE.

    Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential
    absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of
    RTE evaluations \citep{Modest_2016}.

@@

    At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption
    coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG)
    model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model. These models were chosen for their relevance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

@@

    Table~\ref{t:models} summarizes RadLib's three radiative property models and the thermodynamic conditions under
    which they apply.

    \begin{table}
        \caption{Summary of radiative property models in RadLib.}
        \label{t:models}
        \centering
        \resizebox{\textwidth}{!}{
            \begin{tabular}{l l l l}
                \hline
                Model & T range (K) & P range (atm) & Refs.   \\
                \hline
                PM      & 300\textendash 2500 & 1                   & \cite{TNF} \\
                WSGG    & 300\textendash 2400 & 1                   & \cite{Bordbar_2020,Bordbar_2014} \\
                RCSLW   & 300\textendash 3000 & 0.1\textendash 50   &  \cite{Solovjov_2017} \\
                \hline
            \end{tabular}
        }
    \end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    The Planck Mean (PM) model is the simplest of the three models implemented. This model assumes a single gray gas
    (with no transparent gas)
    and computes the absorption coefficient as a function of temperature, pressure, and gas composition.

@@

    For each species, the PM model provides the absorption coefficient as fourth or fifth order polynomial fits in one
    or two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
    Ultimately, the model accommodates temperatures between 300 K and 2500 K. See
    \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
    The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas
    (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames
    in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)

@@

    The gray gas weight $a_j$ is the fraction of blackbody emission from the set of wavenumbers $\Delta_j$ that correspond to a given cross-section band $j$. Weights are computed using the absorption line blackbody distribution function (ALBDF) \cite{Pearson_2014}, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorption cross sections smaller than an arbitrary absorption cross-section $C$:
%
    \begin{linenomath}
        \begin{equation}
            \label{e:albdf}
            F(C,\BS{\phi},T) = \frac{1}{\sigma T^4}\int_{\{\eta:\,C_\eta(\eta,\BS{\phi})<C\}}E_b(\eta,T)d\eta,
        \end{equation}
    \end{linenomath}
%
    where $\phi$ represents the thermodynamic state, $\sigma$ is the Stefan-Boltzmann constant, $T$ is temperature, and $E_b(\eta,T)$ is the blackbody emission at a given wavenumber $\eta$ and temperature $T$.
    As a result, a specific gray gas weight $a_j$ can be calculated as the difference between the ALBDF values at its cross-section boundaries:
%
    \begin{linenomath}
        \begin{equation}
            \label{e:aj}
            a_j = F(\tilde{C}_j,\BS{\phi}, T) - F(\tilde{C}_{j-1}, \BS{\phi},T).
        \end{equation}
    \end{linenomath}
%
%todo: deal with T versus Tb in e:albdf and previous eqn.
    Note that $F$ varies between zero and one and is monotonic in $C$, which permits calculation of an inverse ALBDF $C(F,\BS{\phi},T)$.

@@

    The RCSLW model uses rank correlation as follows.
    Consider Eq.~\ref{e:albdf} evaluated at an arbitrary reference temperature $T_r$ for thermodynamic states $\phi_1$ and $\phi_2$ as detailed above:
% $C=\hat{C}_1$, $\BS{\phi}=\BS{\phi}_1$, $T=T_r$, and again at$C=\hat{C}_2$, $\BS{\phi}=\BS{\phi}_2$, $T=T_r$, where $T_r$ is some reference temperature:
%
    \begin{linenomath}
        \begin{align}
            \label{e:albdf2}
            F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
            F(\hat{C}_2,\BS{\phi}_2,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_2}E_b(\eta,T_r)d\eta.
        \end{align}
    \end{linenomath}
%
    Since $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$ are rank correlated (by definition), $H_1=H_2$ and we have
%
    \begin{linenomath}
        \begin{equation}
            \label{e:FeqF}
            F(\hat{C}_1,\BS{\phi}_1,T_r)=F(\hat{C}_2,\BS{\phi}_2,T_r).
        \end{equation}
    \end{linenomath}
%
    Recall that the ALBDF can be inverted, so if $\hat{C}_1$ and $\BS{\phi}_1$ are known, we can compute $F=F(\hat{C}_1,\BS{\phi_1},T_r)$ and then invert $F$ to obtain $\hat{C}_2$ at $\BS{\phi}_2$. Note that Eq.~\ref{e:FeqF} holds for arbitrary states $\BS{\phi}_1$ and $\BS{\phi}_2$, so any known $F=F(C,\BS{\phi},T)$ can be inverted to get $C$ at the corresponding state $\BS{\phi}$.

@@

    The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, \texttt{lib} containing library files for each interface, \texttt{cmake} with relocatable CMake files for downstream usage, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
    \begin{itemize}
        \item \texttt{rad\textunderscore planck\textunderscore mean.h},
        \item \texttt{rad\textunderscore wsgg.h},
        \item \texttt{rad\textunderscore rcslw.h},
        \item \texttt{rad\textunderscore module.mod}.
    \end{itemize}
%
    The C++ and Fortran libraries in the \texttt{lib} folder are
    \begin{itemize}
        \item \texttt{libradlib.a},
        \item \texttt{libradlib\textunderscore fortran.a}.
    \end{itemize}
%
    This folder also contains the Python module. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation.

@@

    Table~\ref{t:examples} summarizes the example cases. Each case is labeled according to its source---Solvojov et al. \cite{Solovjov_2017} (S), Bordbar et al. \cite{Bordbar_2020} (B), or Solovjov et~al. \cite{Solovjov_2001} (Sb)---and the number of each example corresponds to the example number in its respective reference. Each example case consists of one or more gas layers (``slabs'') bounded by black walls.
    Example S1 consists of two adjacent gas layers with identical species compositions: one hot layer of constant thickness and one cold layer of varying thickness.
    In Example S2, the two gas layers are isothermal but differ in the value of the \ce{CO2} mole fraction, where the layer thickness of the ``thin'' slab (with the smaller \ce{CO2} mole fraction) varies.
    Example S3 applies parabolic temperature and \ce{H2O} mole fraction profiles across a single gas layer.
    Example S4 divides the gas into three equally-spaced layers and applies a triangular temperature profile to the middle layer and a constant temperature to the two outer layers.
    Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K applied to a single gas layer of constant composition.
    Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $x_{CO2}=1-x_{H2O}$).
    Example Sb1 consists of a single gas with a uniform temperature and composition profile and soot radiation.
%
    \begin{table}
        \caption{Summary of example cases. All cases use $P=1$ atm and black walls.}
        \label{t:examples}
        \centering
        \resizebox{\textwidth}{!}{
            \begin{tabular}{c l l c c c c}
                \hline
                Example & T(K)                             & $x_{H2O}$  $x_{CO2}$ (mole frac.)               & L (m)   & $T_{walls}$ (K) & Ref.                 \\
                \hline
                S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$ & $x_{CO2}=0.1$, $x_{H2O}=0.2$ & 0.5-2.5 & cold, cold
                & \cite{Solovjov_2017}
                \\
                S2      & T=1000                           & $x_{CO2}(x<0.5)=0.4$, $x_{CO2}(x>0.5)=0.1$    & 0.5-2.5 & cold, cold      & \cite{Solovjov_2017} \\
                & & $x_{H2O}=0.0$ & & \\
                S3      & $T(x) = 4000x(L-x)/L^2 + 800$    & $x_{H2O}(x) = 0.8x(L-x)/L^2 + 0.12$           & 1       & 800, 800        & \cite{Solovjov_2017} \\
                & & $x_{CO2}=0$ & & \\
                S4      & middle third triangular to 2500  & $x_{H2O}=0.1$, $x_{CO2}=0$                    & 0.3     & 500, 500        & \cite{Solovjov_2017} \\
                S5      & $T(x) = 1000 + 500\cos(\pi x/L)$ & $x_{H2O}=0.1$, $x_{CO2}=0$                    & 2       & 1500, 500       & \cite{Solovjov_2017} \\
                B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$ & $x_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$
                & 1
                & 400, 400
                & \cite{Bordbar_2020}
                \\
                & & $x_{CO2}=1-x_{H2O}$ & & \\
                Sb1     & $T = 1000$                       & $x_{H2O} = 0.2$, $x_{CO2}=0.1$, $x_{CO}=0.03$ & 1       & cold, cold      & \cite{Solovjov_2001} \\
                \hline
            \end{tabular}
        }
    \end{table}
%

@@

    Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}. These plots are included to demonstrate the examples that are provided with the code, and to compare the models to give an indication of their relative accuracy. In all examples, the RCSLW model data is computed using four gray gases ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Example S5, in which the number of gray gases in the RCSLW model is varied. The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature.
%
    \begin{figure}
        \begin{center}
            \begin{tabular}{c c}
                Example S1                                      & Example S2 \\
                \includegraphics[width=2.75 in]{fig_ex_S1.pdf} &
                \includegraphics[width=2.75 in]{fig_ex_S2b.pdf} \\
                Example S3                                      & Example S4 \\
                \includegraphics[width=2.75 in]{fig_ex_S3a.pdf} &
                \includegraphics[width=2.75 in]{fig_ex_S4a.pdf} \\
                Example S5                                      & Example B3 \\
                \includegraphics[width=2.75 in]{fig_ex_S5c.pdf} &
                \includegraphics[width=2.75 in]{fig_ex_B3.pdf}
            \end{tabular}
            \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}. In Examples S2 and S5, $n$
                refers to the number of gray gases considered.}
            \label{f:examples}
        \end{center}
    \end{figure}
%
    \begin{figure}
        \begin{center}
            \includegraphics[width=5.5 in]{fig_ex_Sb1.pdf}
            \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
            \label{f:exSb1}
        \end{center}
    \end{figure}
%

    In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data. The results show that the PM model tends to exaggerate the trends displayed by the other models. The PM data mimics the shape of the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity. For the PM model in Example S5, $Q$ varies from around -80~kW/m$^3$ at $x=0$ to a peak of 200~kW/m$^3$ at x=$1.5$~m and drops to~100 kW/m$^3$ at $x=2$~m.
    In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36 in the thick and thin layers, respectively. These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
    Example S3 illustrates that the PM model tends to overpredict radiative heat loss at hight temperatures, which has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.

@@

    The RadLib model was coupled to the Fire Dynamics Simulator (FDS) code developed at NIST \cite{FDS}. FDS is
    written in Fortran, and the Fortran interface of Radlib was used for simulations. FDS includes several radiative
    models, but the spectral WSGG model coupled to a finite volume discrete ordinates model is used here. This was
    done by editing the \texttt{radi.f90} file in FDS. A \texttt{use rad\textunderscore module} statement is included
    and the FDS functions \texttt{A\textunderscore WSGG} and \texttt{KAPPA\textunderscore WSGG} are replaced with calls
    to RadLib's \texttt{get\textunderscore k\textunderscore a\textunderscore oneband}. The \texttt{oneband} version was
    used because FDS does an outer iteration over the bands/gases, computing properties at a given band for each grid point.

@@

    RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property models in CFD simulations. At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. Each of the implemented models has been validated and the library's structure and functionality has been outlined. The library can be expanded to include additional property models.
